---
title: "Midpoint Deliverable"
author: "Shari Sung" "Xin Zhang"
date: "11/17/2019"
output: html_document
---

```{r setup, include = FALSE}
source("analysis.R")
source("airbnb_project_interactive_map.R")
source("scripts/chart.R")
library("knitr")
```

## Purpose of the project
We wanted to analyze airbnb data from ten major cities in the United States collected in 2019 to come up with a specific airbnb tourist guide that could give travelers more insights on which airbnb to choose and which host they could rely on.

## Source of the data of the project
Source of data collected: http://insideairbnb.com/get-the-data.html


## Aggregated chart 
Here are the airbnbs hosts that have the **top ten highest rating** near Pike Place Market in 2019. These hosts have been verified as superhosts, have a 100% response rate, responses within an hour, and have their real identity verified through by Airbnb officials. 

```{r best_hosts_near_pike, echo = FALSE}
# Show the top 10 table (specifying the column names to display)
kable(best_hosts_near_pike,
      col.names = c("Host Name", "Item Name", "Host Ratings"))
```

## Interactive map 
```{r map, echo=FALSE}
map
```
The reason why we wanted to use an interactive graph is because we wanted to show to location of each airbnb listing and the neccessary information tied to the listings, such as the house owner of the listing, price per night and room type, etc.

## Bar Graph
```{r bar_chart, echo=FALSE}
bar_chart_function(data)
```
This chart contains infomation of each neibourhood's average aribnb price. It's very helpful when people are planning their travel budget. You can search for housing result in different neigbourhoods based on your budget. The average airbnb price in Downtown is the most expensive in Seattle which is $288.4471 per night and Delridge is the least expensive with only $100.6805 per night.

